---
title: "Telehealth"
author: "Maria Prokofieva"
date: "06/02/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE}
library(XML)
library(tidyverse)
```

### Telehealth Information

From 1 January 2022, patient access to telehealth services will be supported by continued MBS arrangements. The continued arrangements build on the **temporary telehealth items** introduced as part of the Government's response to the COVID-19 pandemic, and will continue to enable all Medicare eligible Australians to access **telehealth (video and phone)** services for a range of (out of hospital) consultations that can also be provided in person.

*MBS telehealth items* will continue to be available to GPs, medical practitioners, specialists, consultant physicians, nurse practitioners, participating midwives, allied health providers and dental practitioners in the practice of oral and maxillofacial surgery.

#### Things to consider:

- new ‘30/20 rule'?

From 1 July 2022, a new prescribed pattern of service (a ‘30/20 rule’) will apply to telephone attendances provided by consultant physicians and GPs. This was introduced on 1 January 2022, but will now be deferred. 

Under these new arrangements, a consultant physician or GP who provides 30 or more phone attendances on each of 20 or more days in a 12-month period would be referred to the *Professional Services Review* (PSR) https://www.psr.gov.au/ 

All Victorian SARS-CoV-2 cases by local government area, postcode and acquired source
https://discover.data.vic.gov.au/dataset/all-victorian-sars-cov-2-cases-by-local-government-area-postcode-and-acquired-source

MBS telehealth items:

- data
[File released on 19 January 2021](http://www.mbsonline.gov.au/internet/mbsonline/publishing.nsf/Content/4601E2A66F2AAB6ACA258797000C2F26/$File/mbs-xml-20220118.XML)

**Note**: 

The file includes 

- includes temporarily reinstating 75 **telehealth** and phone services to enable practitioners to support their patients during the current increase in Omicron COVID-19 cases.
This file incorporates the 1 January 2022 changes and replaces the file released on 23 December 2021. 

- updated rapid antigen testing to expand the service described in item 93715 (=assessment and management of a person with COVID-19 infection of recent onset)

View the `.csv` version 

- data file [here](https://raw.githubusercontent.com/maria-pro/MBS/main/telehealth_012022.csv)

- item map file [here](https://github.com/maria-pro/MBS/raw/main/item_map_01_2022.csv)

- item description file [here](https://github.com/maria-pro/MBS/raw/main/Item_Descriptors.csv)

```{r eval=FALSE, echo=FALSE}
xml_link<-"http://www.mbsonline.gov.au/internet/mbsonline/publishing.nsf/Content/4601E2A66F2AAB6ACA258797000C2F26/$File/mbs-xml-20220118.XML"

data<-xmlToDataFrame(xml_link)
write_csv(data, file="telehealth_012022.csv")
```

```{r message=FALSE}
data<-read_csv("telehealth_012022.csv")%>%
  mutate_if(is.character, as.factor)%>%
  mutate(DerivedFee=as.character(DerivedFee))%>%
  mutate(
    across(c("Category", "SubGroup", "SubHeading"),
           factor)
    )
```

Quick data summary:
```{r echo=FALSE}
skimr::skim(data)
```

- The item map from [here](http://www.mbsonline.gov.au/internet/mbsonline/publishing.nsf/Content/1BC94358D4F276D3CA257CCF0000AA73/$File/20220301_MBSONLINE_IMAP%2021JAN22.TXT) converted to csv

```{r echo=FALSE}
item_map<-read_csv("item_map_01_2022.csv")

skimr::skim(item_map)
```

Item Descriptors file from [here](http://www.mbsonline.gov.au/internet/mbsonline/publishing.nsf/Content/1BC94358D4F276D3CA257CCF0000AA73/$File/20220301_MBSONLINE_DESC.TXT)
```{r echo=FALSE}
item_descr<-read_csv("Item_Descriptors.csv")

skimr::skim(item_descr)
```